The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-08 ms.tex
2.3 update

We also neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.  However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instabilities (e.g.~\citealt{McCourt+12}) that our 1D
time-independent model cannot account for self-consistently anyways.  A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).

>>>>

Radiative cooling contributes an additional term to equation (\ref{eq:dsdt}) of the form
\be
\dot{q}_{\rm rad} = -\Lambda(T)n^{2},
\label{eq:qdot_rad}
\ee
where $n = \rho/\mu m_p$ is the gas number density and $\Lambda(T)$ is the cooling function.  We neglect radiative cooling in our baseline calculations, despite the fact that this is not justified when the wind heating $\vwO$ is low and/or stellar mass loss rate $\eta$ is high.  However, once radiative cooling becomes important compared to other sources of heating and cooling, its presence leads to thermal instabilities (e.g.~\citealt{McCourt+12}) that our 1D
time-independent model cannot account for self-consistently anyways.  A main goal of this work is to use analytic and numerical solutions neglecting radiation to ascertain over what range of physical conditions cooling instabilities are most likely to develop ($\S\ref{sec:cooling}$).
